A Journey from Wild to Textbook Data to Reproducibly Refresh the Wages Data from the National Longitudinal Survey of Youth Database

### 2022-06-07 paper/cover-letter/cover-letter.Rmd
Add response to the editors.

Please consider the revised version of our paper titled "The Journey from Wild to Textbook Data: A Case Study from the National Longitudinal Survey of Youth" for the JDSDE Special Issue on "Teaching Reproducibility and Responsible Workflow".

The paper is co-authored by Prof. Di Cook, Dr Emi Tanaka, Kate Hyde and Dr Nick Tierney. We believe it is a good fit for the special issue because it covers various aspects of data management and curation component of data acumen, including data preparation and cleaning, missing and conflicting data. The code to reproduce the data cleaning, and make further updates of the resulting data is provided.

We also provide the response of editor and reviewers' comments. We also agree if you share this paper with the discussant for this special issue.

>>>>

Please consider the second revision of our paper titled "The Journey from Wild to Textbook Data: A Case Study from the National Longitudinal Survey of Youth" for the JDSDE Special Issue on "Teaching Reproducibility and Responsible Workflow".

The paper is co-authored by Prof. Di Cook, Dr Emi Tanaka, Kate Hyde, and Dr Nick Tierney. We believe it is a good fit for the special issue because it covers various aspects of data management and curation component of data acumen, including data preparation and cleaning, missing and conflicting data. The code to reproduce the data cleaning, and make further updates of the resulting data is provided. We also believe that this data fits for teaching longitudinal data-purpose.

We also provide the response of editor and reviewers' comments.
